Approximate Network Matching

### 2024-02-19 paper.qmd
add short section on definitions

>>>>

## Definitions

The purpose of this section is to provide clear and concise definitions of terminologies used in the description of this algorithm.

We will use the simple feature access standards definitions of geometric primitives for the sake of consistency. In our algorithm we make extensive use of **Line** and **LineString** geometric primitives. A Line is defined by two **Point**s that are (x, y) coordinate pairs. A LineString is composed of 2 or more Points and "each consecutive pair of Points defines a Line segment." (@sfa FIXME cite). Each LineString is referred to as a **feature**. An array of features is referred to as a **FeatureCollection** (@geojson_spec).

The objective of this algorithm is to identify matches between two LineString FeatureCollections and measure the length of the match. A **match** is a correspondence between features of separate FeatureCollections (@lei_lei_19).

The terminology to refer to the two FeatureCollections is inconsistent. For example, Zhang (@zhang_2009) refers to the two FeatureCollections as the **reference** and **target** whereas the Java Conflation Suite (JCS) (@jcs) refers to these as the **reference** and **subject**.

We will use the terms _reference_ FeatureCollection and _subject_ FeatureCollection. The objective of the matching algorithm is to match features _from_ the subject _to_ the reference. Often the reference is a more detailed and known collection of features.

In the process matching features, **candidate**s are found. A candidate is a subject feature that may correspond to a reference feature. If a candidate passes tests, it is then deemed a match. After matches have been found, attributes from the source feature are often transferred to the reference feature. This process of attribute transfer is referred to as **integration**.
